---
title: ''
author: "KN"
date: '`r Sys.Date()`'
output: html_document
---


About
=====
- Questionnaire through Lancers, conducted in September, 2016.
- 104 participants (after eliminating duplicate subjects and one subject who chose 5 only)
- 5-point Likert scale
- Target items: 
    + e 16 
    + dative 6
    + good fillers 21, bad fillers 5
48 in total

Conditions:  
e (a{mb/im} x b{ex/on})
mobile object x extended causation  
サッカー選手が左足をゴールポストにぶつけた。  
immobile object x extended causation   
サッカー選手がゴールポストを左足にぶつけた。  
mobile object x onset causation
サッカー選手がサッカーボールをゴールポストにぶつけた。  
immobile object x onset causation  
サッカー選手がゴールポストをサッカーボールにぶつけた。  


##### Load libraries

```{r}
library(lme4)
library(xtable)
library(plyr)
library(ggplot2)
library(reshape)
library(gdata)      
library(MASS)
```


##### Declare the expt name that is relevant.
```{r}
ex<-"e"

# plot labels
#ab<-"NPI"
#cd<-"nonNPI"
#ac<-"Distant"
#bd<-"Local"

```


##### Load data:

```{r}
alldata<-read.csv("newdata.csv")
```







Subj exclusion
==============
##### before trimming
Subject number before trimming
```{r}
unique(alldata$subj)
length(unique(alldata$subj))
```


##### trim

```{r}
data<-alldata
data<-subset(data,subj!=c(9999))
unique(data$subj)
length(unique(data$subj))
```



##### standardized rating

```{r}
Zrate<-c()
for(i in unique(data$subj)){   
  # それぞれのsubj ratingを抜き出し
  mySubjRating <- data[data$subj==i,];
  # standardize
  mySubjRating<-data.frame(mySubjRating,ZS=scale(mySubjRating$rating))
  # それを蓄積
  Zrate<-rbind(Zrate,mySubjRating)
}

data <- merge(data,Zrate,all=T);

# sort when messed up
data <- data[order(data$subj,data$expt,data$item),]
rownames(data) <- c(1:nrow(data))
```


Isolate the data from the relevant experiment
=============================================
```{r}
d<-subset(data,expt==ex)
d<-subset(d,item%in%c(9:16))
unique(d$expt)
unique(d$item)
```

Summary
====================

##### Make sure factors are treated as factors
```{r}
d$subj<-factor(d$subj)
d$expt<-factor(d$expt)
d$item<-factor(d$item)
d$a<-factor(d$a)
d$b<-factor(d$b)
```


## Summary (interim)

のちにtrimmingをする（かもしれない）ので，このファイルの最後でもういちどサマリーとプロットの最終盤を生成します。

##### Extract data for summary



##### summary
```{r}
ddply(d, .(a,b), summarise, N=length(subj), mean=mean(rating), sd=sd(rating), se=sd/sqrt(N))
ddply(d, .(a,b), summarise, N=length(subj), mean=mean(ZS), sd=sd(ZS), se=sd/sqrt(N))
```


##### graph
http://www.cookbook-r.com/Graphs/Bar_and_line_graphs_(ggplot2)/

```{r}
df<-ddply(d, .(a,b), summarise, N=length(subj), mean=mean(rating))
df

g <- ggplot(df,aes(x=a, y=mean, fill=b))
g <- g + geom_bar(stat="identity", position=position_dodge(), color="black")
g <- g +scale_fill_manual(values=c("gray", "gray"))
print(g)

# A bar graph
g <- ggplot(df, aes(x=a, y=mean, fill=b)) 
g <- g + geom_bar(colour="black", stat="identity",
             position=position_dodge(),
             size=.3)                        # Thinner lines
g <- g +  scale_fill_hue(name="Causation type")      # Set legend title
g <- g +  xlab("Object type") + ylab("Mean ratings") # Set axis labels
g <- g +  ggtitle("Mean ratings")     # Set title
g <- g +  theme_bw()
g <- g +  theme(legend.position=c(.2, .7))           # Position legend inside
g

# A line graph
g <- ggplot(df, aes(x=a, y=mean, group=b, shape=b, colour=b)) 
g <- g + geom_line(aes(linetype=b), size=1)     # Set linetype
g <- g  + geom_point(size=3, fill="white")         # Use larger points, fill with white
g <- g  + expand_limits(y=1)                       # Set y range to include 0
g <- g  + scale_colour_hue(name="Object type",      # Set legend title
                     l=30)                  # Use darker colors (lightness=30)
g <- g + scale_shape_manual(name="Object type",
                       values=c(22,21))      # Use points with a fill color
g <- g + scale_linetype_discrete(name="Object type")
g <- g + xlab("Causation type") + ylab("Mean ratings") # Set axis labels
g <- g + ggtitle("Mean ratings")     # Set title
g <- g + theme_bw()
g <- g +  theme(legend.position=c(.8, .4))           # Position legend inside
                                               # This must go after theme_bw
g


```


Analyses
========


### Analysis 



Coding factors (with centering)
-------------------------------

##### CONDITIONS:

```{r}
d$int<-ifelse(d$a=="mb"&d$b=="ex",1,ifelse(d$a=="im"&d$b=="on",1,-1))

g <- ggplot(d, aes(x=int, y=rating))
g <- g + geom_jitter(width=1)
g <- g + geom_point(shape=1, fill="gray")    # Use hollow circles
#g <- g + geom_boxplot()
g <- g + geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
g


d$obj<-ifelse(d$a=="mb",1,-1)
d$caus<-ifelse(d$b=="ex",1,-1)

g <- ggplot(d, aes(x=obj, y=rating))
g <- g + geom_jitter(width=1)
g <- g + geom_point(shape=1, fill="gray")    # Use hollow circles
#g <- g + geom_boxplot()
g <- g + geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
g

g <- ggplot(d, aes(x=caus, y=rating))
g <- g + geom_jitter(width=1)
g <- g + geom_point(shape=1, fill="gray")    # Use hollow circles
#g <- g + geom_boxplot()
g <- g + geom_smooth(method=lm,   # Add linear regression line
                se=FALSE)    # Don't add shaded confidence region
g
```



##### Max model
```{r}
mm<-lmer(rating~a*b+
           (a*b+1|subj)+(a*b+1|item),
           control=lmerControl(optimizer="bobyqa"),
           d)
summary(mm)

mm<-lmer(rating~obj*caus+
           (obj*caus+1|subj)+(obj*caus+1|item),
           control=lmerControl(optimizer="bobyqa"),
           d)
summary(mm)

mm<-lmer(ZS~a*b+
           (a*b+1|subj)+(a*b+1|item),
           control=lmerControl(optimizer="bobyqa"),
           d)
summary(mm)

mm<-lmer(ZS~obj*caus+
           (obj*caus+1|subj)+(obj*caus+1|item),
           control=lmerControl(optimizer="bobyqa"),
           d)
summary(mm)

```



